---
title: "Tidy Data"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load Library


```{r}

library()

```


## Creating a Tibble

- Tibble is a modern version of data frame.
- They do less (eg: doesn't change variable names) and 
  talk more (eg: warns when variable doesn't exists).

```{r}

# tibble with 4 cols, 3 rows
data <- tibble(
  id = 1:2,
  x = c("a", "b"),
  y = c("c", "d"),
  z = c("e", "f")
)
```


## Pivoting - Wide to Long

```{r}
long <- pivot_longer(     ,          
                     cols = ,        
                     names_to = "",  
                     values_to = ""    
                     )


long

```


## Pivoting - Long to Wide

```{r}
wide <- pivot_wider(     ,        
                    names_from = , 
                    values_from =     
)


wide
```


## Your Turn - 01

- Convert table4a data into tidy format and
save it into table_a.

```{r}

table_a <- table4a




table_a

```


## Your Turn - 02

- Convert table4b data into tidy format and 
save it into table_b.

```{r}

table_b <- table4b





table_b

```


## Your Turn - 03

## Join table_a and table_b into df.

```{r}
library(dplyr)


df

```


## Your Turn - 04


- What is the average rate of cases in year 2000?

```{r}









```
